MSDS6372Project1

### 2021-01-25 MSDS6372Project1.Rmd
forgot to save rmd

# Adjust column names - get ride of - and space in the column names to make analysis easier
# Also make column names more uniform
CarData = CarData %>%
  rename(
    EngineFuelType = Engine.Fuel.Type,
    EngineHP = Engine.HP,
    EngineCylinders = Engine.Cylinders,
    TransmissionType = Transmission.Type,
    DrivenWheels = Driven_Wheels,
    NumberOfDoors = Number.of.Doors,
    MarketCategory = Market.Category,
    VehicleSize = Vehicle.Size,
    VehicleStyle = Vehicle.Style,
    HighwayMPG = highway.MPG,
    CityMPG = city.mpg,
    HighPerformance = `High-Performance`,
    FactoryTuner = `Factory Tuner`,
    FlexFuel = `Flex Fuel`,
    N_A = `N/A`
  )

# Look at summary of data
summary(CarData$VehicleStyle)
# Look at missing Data if any
# missingData = CarData[rowSums(is.na(CarData)) > 0,]
# missingData
# dim(missingData)
write.csv(CarData,"CleanedCarData.csv",row.names = FALSE)

>>>>

# Adjust column names - get ride of - and space in the column names to make analysis easier
# Also make column names more uniform
CarData = CarData %>%
  rename(
    EngineFuelType = Engine.Fuel.Type,
    EngineHP = Engine.HP,
    EngineCylinders = Engine.Cylinders,
    TransmissionType = Transmission.Type,
    DrivenWheels = Driven_Wheels,
    NumberOfDoors = Number.of.Doors,
    MarketCategory = Market.Category,
    VehicleSize = Vehicle.Size,
    VehicleStyle = Vehicle.Style,
    HighwayMPG = highway.MPG,
    CityMPG = city.mpg,
    HighPerformance = `High-Performance`,
    FactoryTuner = `Factory Tuner`,
    FlexFuel = `Flex Fuel`,
    N_A = `N/A`
  )
# Look at HighwayMPG outlier identified by Nicole
CarData %>% filter(HighwayMPG==354)
# Change observation HighwayMPG 354 to 34
CarData$HighwayMPG = ifelse(CarData$HighwayMPG==354,34,CarData$HighwayMPG)

# Look at summary of data
summary(CarData$VehicleStyle)
str(CarData)
# Look at missing Data if any
# missingData = CarData[rowSums(is.na(CarData)) > 0,]
# missingData
# dim(missingData)
write.csv(CarData,"CleanedCarData.csv",row.names = FALSE)
